Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

    \vspace{4mm}
    \figcapup
    \caption{Result comparison on $k$-SJ problem for a constant $k$}
    \label{tab:results-com}
    \figcapdown \vspace{-5mm}
\end{table}

@@

This section will first define some notions frequently used in our presentation and then introduce several  geometry problems, whose solutions will serve as building bricks for our $k$-SJ algorithm.

>>>>

    \vspace{4mm}
    \figcapup
    \caption{Result comparison on $k$-SJ problem for a constant $k$}
    \label{tab:results-com}
    \figcapdown \vspace{-3mm}
\end{table}

@@

This section will first introduce some definitions and notations to be frequently used in our presentation and then formulate several computational geometry problems, whose solutions will serve as building bricks for our $k$-SJ algorithm.
